---
title: "ESM 206 Lab 8"
author: "Evie Vermeer"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)

```

```{r}
homes <- read_csv(here("data","slo_homes.csv"))

```



Make a subset called homes_sub that only contains observations where the city is:
Make sure you are not filtering ("","","") because it places an emphasis on sequential 


```{r}

homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo","Arroyo Grande", "Atascadero","Santa Maria-Orcutt"))

#To make sure your filter worked and view your data, use "unique"


unique(homes_sub$City)
```


Do a little exploring of our data...

Summary statistics for home price, based on city and sale status

Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sales status 

```{r}
homes_sub_stats <- homes_sub %>% 
  
group_by(City, Status ) %>% 

summarize(mean_price = mean(Price, na.rm = TRUE),
         (sd_price = sd(Price)))

# If you don't actually want to run this code, you can set eval = FALSE in code chunk 

ggplot(data = homes_sub, aes(x=Price)) +
  geom_density(aes(color= City, fill = City), alpha = .3)+
  scale_x_continuous(limits= c(0,3e6))

```

Explore the relationship (visually) between square footage and home price. Change the point color by city and the point shape by sale status

```{r}
ggplot(data = homes_sub, aes(x=SqFt, y=Price))+
  geom_point(aes(color=City, shape=Status)) +
  geom_smooth(method="lm", color="green")


```






